\chapter{OBJECTIVE AND SCOPE}

\section{Objectives}

\subsection{Providing access to different video lecture that is stored at server without downloading onto device.}
Virtual classroom project provides the facility to access different video lectures present on server without downloading it. The video lecture list can be displayed according to branch as well as year of student.

\subsection{Project provides facility of bookmarking.}
The bookmarking facility is nothing but the student is able to see video lectures which he had already seen to certain time interval. After that student may continue to saw same video lecture.

\subsection{Admin can delete the video lectures and also user accounts.}
Admin have authority to delete the video lectures present on server to reduce the load on server. Admin can also delete the user accounts that are passed out. 

\subsection{Providing one option to store the important lectures in the SD card in case there is loss of Wi-Fi connectivity.}
               If there is loss of Wi-Fi connection in that case user can save the video lectures into the SD card.



\section{Scope}
\begin{itemize}
\item User can view the currently active video lectures present in server without downloading it. 
\item The additional feature of this project is bookmarking a video.       
\item Staff can upload the video and also record the video.
\end{itemize}

\section{Out of Scope}
\begin{itemize}
\item Support of all video formats on android mobile client.
\item Adjusting the video quality and aspect ratio according to network strength.
\item User can adjust the speed of the buffered video lecture according to the need.
\item Shows the list of related video lecture at the end of current video lecture.
\end{itemize}
