\chapter{TESTING}
\section{What is Software Testing}

Software testing is the process of analyzing or operating software for the purpose of finding bugs.
Testing can be described as a process used for reveling defects in software, and for establishing that the software has attained a specified degree of quality with respect to selected attribute.The fundamental objective of testing is to find defects ,as early as possible and get them fixed.

{\bf Software Testing Process}
\begin{itemize}
\item Test Planning
 high level plans which list test objectives, test approach, measurement criteria along with test schedule and resources.
 \item Test Design
create test cases, identify test cases for automation(if applicable),prioritize test cases and finalize test iterations.
\item Test Implementation
Create test scripts using automated testing tools.
\item Test Execution
Execute the test cases on the test environment and test reports.
\item Test analysis
Use test and project metrics to calculate key indicators. The data usually will be obtained from your defect tracking system.
\item Postmortem reviews
Discuss lessons learnt and identify strategies which will prevent such problems in future.
\end{itemize}
\section{Test methods}

\subsection{Black box testing }
It is also called as functional testing, it is the process of giving the input to the system and checking the output of the system.Without bothering about the system that how the system generates the output. It is also called as Behavior testing.
\begin{itemize}
\item Approach to testing where the program is considered as a “Black Box”.
\item Testing based solely on analysis of requirements  user specification, user documentation etc.
\item The test cases are based on the specifications.
\item Black box testing techniques apply to all levels of testing.
\item Test planning and design can begin early in the software process.
\item Tests are done from a users point of view.
\end{itemize}
\subsection{White Box Testing}
White box testing or structural testing considers facets like programming style, control method, source language, database design. A test for remote monitoring routine can be an example of structural test. This type of testing helps to uncover defects at structural level. The tests go below the top or functional layer to uncover the defects.
\begin{itemize}
\item Testing that takes into account internal structure and flow of a system or component.
\item The testing is based on code structure or the algorithm.
\item White box testing assumes that the procedural design and code is known to the tester.
\item Obliviously test design can be done only after coding is complete.
\item White box tests are inherently finite.
\end{itemize}

\section{Test cases and test data}
\begin{itemize}
\item Test data are inputs that have been devised to test the system.
\item Test cases are inputs and output specification plus a statement of the function under test.
\item Test data can be generated automatically or real. 
\end{itemize}

% Table generated by Excel2LaTeX from sheet 'Sheet1'
\begin{landscape}
\subsection{Test Cases}
\nopagebreak
\begin{center}
\begin{longtable}{|p{0.8cm}|p{2.5cm}|p{3.3cm}|p{7cm}|p{3cm}|p{3cm}|p{1.9cm}|}


\hline
{\bf TC ID}    & {\bf OBJECTIVE}    & {\bf PREREQUISITES
}          &  {\bf STEPS TO BE FOLLOWED}      & {\bf EXPECTED RESULT}                  & {\bf ACTUAL RESULT}              & {\bf REMARK}      \\ \hline
\endfirsthead
   
\multicolumn{7}{c}%
{{\bfseries \tablename\ \thetable{} -- continued from previous page}} \\
    \hline
   {\bf TC ID}    & {\bf OBJECTIVE}    & {\bf PREREQUISITES
}          &  {\bf STEPS TO BE FOLLOWED}      & {\bf EXPECTED RESULT}                  & {\bf ACTUAL RESULT}              & {\bf REMARK}      \\ \hline



\endhead
\hline \multicolumn{7}{|r|}{{Continued on next page}} \\ \hline
\endfoot
\endlastfoot
  1     & Login into the application & User Must be login & 1.User Should be enter the correct user name. & The Application will give an authorized access. & Granted the permissions and redirect to next page & Pass \\
          &       &       & 2.User shold be fill the password in the password field. &       &       &  \\
          &       &       & 3.click on Login button &       &       &  \\ \hline

    2     & Register student into the application & To perform it's operation user must be click on New User button & 1.Enter First Name in FirstName TextField & It will create student account successfully & Give Confirmation message to student about registration  & pass \\ 
          &       &       & 2.Enter Middle Name in MiddleName TextField &       &       &  \\
          &       &       & 3.Enter Last Name in LastName TextField &       &       &  \\
          &       &       & 4.Enter Standard in Standard TextField &       &       &  \\
          &       &       & 5.Enter Brach in Branch TextField &       &       &  \\
          &       &       & 6.Enter Roll No. in RollNo. TextField &       &       &  \\
          &       &       & 7.Enter Password in Password TextField &       &       &  \\
          &       &       & 8.Re-enter Password in ConfirmPassword TextField &       &       &  \\
          &       &       & 9.Enter Security Question in SecurityQuestion TextField &       &       &  \\
          &       &       & 10.Enter Answer of Security Question in Answer TextField &       &       &  \\
          &       &       & 11.Click on Submit Button &       &       &  \\ \hline
    3     & Register staff in application & To perform it's operation staff must be click on New User button & 1. Enter First Name in FirstName TextField & It will create staff account successfully & Give Confirmation message to staff about registration  & pass \\
          &       &       & 2.Enter Middle Name in MiddleName TextField &       &       &  \\
          &       &       & 3.Enter Last Name in LastName TextField &       &       &  \\
          &       &       & 4.Enter Username in UserName TextField &       &       &  \\
          &       &       & 5.Enter Password in Password TextField &       &       &  \\
          &       &       & 6.Re-enter password in ConfirmPassword TextField &       &       &  \\
          &       &       & 7.Enter  Security Question in SecurityQuestion TextField &       &       &  \\
          &       &       & 8.Enter Answer of Security Question in Answer TextField &       &       &  \\
          &       &       & 9.Click on Submit button &       &       &  \\ \hline
    4     & Register Admin in application & To perform it's operation admin must be click on New User button & 1.Enter username in UserName TextField & It will  create admin account successfully & Give Confirmation message to admin about registration & pass \\
          &       &       & 2.Enter password in Password TextField &       &       &  \\
          &       &       & 3.Re-enter pasword  in ConfirmPassword TextField &       &       &  \\
          &       &       & 4.Enter Security Question in SecurityQuestion TextField &       &       &  \\
          &       &       & 5.Enter Answer of security question in Answer TextField &       &       &  \\
          &       &       & 6.Enter Security Key in SecurityKey TextField &       &       &  \\
          &       &       & 6.Click on Submit Button &       &       &  \\ \hline
    5     & View Video & To perform it's operation user must be click on Show Subjectwise Videobutton & 1.User should click on Show Subjectwise video Button & It will show video list \& play particular video & It will show video list \& play particular video & pass \\
          &       &       & 2.User should Click on particular subject in the list &       &       &  \\
          &       &       & 3.User should select particular video for playing video &       &       &  \\ \hline
    6     & Upload Video & To perform it's operation staff must be click UploadVideo  button & 1. Enter standard in Standard TextField & It will upload video on server & After uploading video on server it will confirmation message to staff & pass \\
          &       &       & 2.Enter sunject in Subject TextField &       &       &  \\
          &       &       & 3.click on Select Video button  &       &       &  \\
          &       &       & 4.Select Video from sdcard &       &       &  \\
          &       &       & 5.Click on Upload button &       &       &  \\ \hline
    7     & Record Video & To perform it's operation staff must be click on Record Video button & 1.Click on Record Video button  & Recording complete \& upload that video on server & Recording complete \& upload that video on server & pass \\
          &       &       & 2.Click on start button &       &       &  \\
          &       &       & 3. Click on stop button &       &       &  \\
          &       &       & 4.Click on done button &       &       &  \\
          &       &       & 5.Click on Upload button &       &       &  \\ \hline
    8     & Bookmark video & To perform it's operation user must be click on pause button & 1. Click on show subjectwise videolist button & It will store details of video into the database & It will store details of video into the database  & pass \\
          &       &       & 2.Select particular subject from subject list &       &       &  \\
          &       &       & 3.Select video from video list for playing that video &       &       &  \\
          &       &       & 4.click on Bookmsrk Video button &       &       &  \\ \hline
    9     & Delete Video & To perform it's operation admin must be click on Delete Video button & 1. Click on delete video button & It will delete video from database & It will delete video from database successfully & pass \\
          &       &       & 2.Enter standard in Standard TextField &       &       &  \\
          &       &       & 3.Enter subject in Subject TextField &       &       &  \\
          &       &       & 4.Enter video name in VideoName TextField &       &       &  \\
          &       &       & 5.Click on Delete  Video button &       &       &  \\ \hline
    10    & Delete Account & To perform it's operation admin must be click on Delete Account button & 1.Click on Delete account button & It will delete account from database & It will delete account from database successfully & pass \\
          &       &       & 2.Enter username in UserName TextField &       &       &  \\
          &       &       & 3.Clicks on Delete Account button &       &       &  \\ \hline
   \caption{Test Cases}
\end{longtable}
\end{center}
\end{landscape}





